---
title: "Airbnb NY"
author: "Rodrigo Valdes Ortiz"
date: "4/29/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggpubr)
```

```{r echo=FALSE}
# Load data
listings = read.csv("../results/listings_graph.csv", header=TRUE, sep=",")
listings = listings[listings$review_scores_rating <= 95,] ## I will focus on those who can improve
f_importance = read.csv("../results/feature_importance.csv", header=TRUE, sep=",")

# Create some categorical variables
listings$verifications_cat <-cut(listings$host_verifications, c(0,3,6,9,13), 
                                 labels=c("   (0-3]   ", "   (3-6]   ", "   (6-9]   ", "   (9-13]   "))
```

```{r echo=FALSE}
# Main theme
blank_theme <- theme_minimal()+
  theme(
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=14, face="bold")
  )
```

# Visualization 1: Is there descriptive evidence of factors that might affect review's scores?

The reviews' scores are related to characteristics that host can modify, such as cancellation policy, host response time, and the number of identity verifications. Notice that the distribution of scores is skewed (many observations close to 100). **However, which are the important factors to increase your score? Can you improve your profits if you increase your score?**

```{r echo=FALSE}
## Visualization 1 ##

# Give the order of the factors
listings$cancellation_policy <- factor(listings$cancellation_policy, c('flexible', 'moderate', 'strict', '+strict', '++strict'))
listings$host_response_time <- factor(listings$host_response_time, c('< 1 hour', 'hours','1 day', 'days'))

# Graph about cancellation policy
cancellation = ggplot(listings, aes(factor(cancellation_policy), 
                                    review_scores_rating, fill = cancellation_policy)) +
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge") + 
  blank_theme +
  labs(x = "Cancellation policy", y = "Reviews rating") + 
  theme(legend.position = "none", 
        axis.text.x = element_text(colour="grey20",size=6.5, angle=90, face="bold"),
        axis.title.x = element_text(colour="grey20",size=9, face="bold"))

# Graph about respond time
respond_time = ggplot(listings, aes(factor(host_response_time), review_scores_rating, fill = host_response_time)) +
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge") + 
  blank_theme +
  labs(x = "Host response time", y = "") + 
  theme(legend.position = "none",
        axis.text.x = element_text(colour="grey20",size=7.5, angle=90, face="bold"),
        axis.title.x = element_text(colour="grey20",size=9, face="bold"))

# Graph about number of identity verifications of the host
verifications = ggplot(listings, aes(verifications_cat, review_scores_rating, fill = verifications_cat)) +
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge") + 
  blank_theme +
  labs(x = "Number of host verifications", y = "") + 
  theme(legend.position = "none", 
        axis.text.x = element_text(colour="grey20",size=7.7, angle=90, face="bold"),
        axis.title.x = element_text(colour="grey20",size=9, face="bold", margin = margin(b=4)))

ggarrange(cancellation, respond_time, verifications, ncol = 3, nrow = 1)

```

# Visualization 2: Feature Importance

According to a preliminary analysis of a random forest model, the most important features to increase your score are the number of reviews, reviews per month, super host, and host listings count. However, many of these variables are correlated with the experience of the host. Then, a more profound analysis is needed. This plot generates two hypothesis: **1) time and experience increase your score, 2) only excellent host stay on the platform for a long time, 3) strategies to increase your number of visits and reviews might have positive effects.**

```{r echo=FALSE}
## Visualization 2

f_importance$feature <- factor(f_importance$feature, f_importance$feature)

ggplot(f_importance, aes(x=feature)) +
  geom_bar(aes(y=importance), position="dodge",stat="identity", fill="royalblue2")  + blank_theme + 
  theme(legend.position = "none") +
  labs(x = "Feature", y = "Importance") +
  ggtitle("Most import features") +
  coord_flip() +
  theme(legend.position = "none", 
        axis.text.x = element_text(colour="grey20",size=10, angle=0, face="plain"),
        axis.text.y = element_text(colour="grey20",size=10, angle=0, face="bold"),
        axis.title.x = element_text(colour="grey20",size=12, face="bold"),
        axis.title.y = element_text(colour="grey20",size=12, face="bold"),
        plot.title = element_text(hjust = 0.5))

```

